Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
minor tweaks to ms/comment cleanup

d <- left_join(project_plan, project_data_summary, by = c("project_key")) %>%
  rowwise() %>%
  mutate(fidelity = (replication_fidelity_MCF + replication_fidelity_ES) / 2) %>%
  ungroup
```

@@

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have an effect on the results.

@@

```{r}
d$high_fidelity <- d$fidelity > median(d$fidelity)
# table(d$replicated_TA,d$replicated_student) # Make prettier
#mean(d$replicated_team)

@@

outcomes <- bind_rows(replicated, turk, fidelity, open_materials) 
names(outcomes) <- c("No","Partial","Full", "Mediator","Value")
outcomes <- outcomes %>%
  select(Mediator, Value, No, Partial, Full)

# print(xtable(outcomes), include.rownames = FALSE)
```

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{rl|ccccccc} -->
<!--   \hline -->
<!-- \multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\ -->
<!--   \hline -->
<!--    &  & No & Yes & Yes & No & No & Some & Yes \\  -->
<!--   Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\  -->
<!--   Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\  -->
<!--   No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\  -->
<!--   \hline -->
<!--   Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\ -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest. High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).} -->
<!-- \end{table} -->

>>>>

d <- left_join(project_plan, project_data_summary, by = c("project_key")) %>%
  rowwise() %>%
  mutate(fidelity = (replication_fidelity_MCF + replication_fidelity_ES + replication_fidelity_RH) / 3) %>%
  ungroup
```

@@

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus). The mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have had an effect on the results.

@@

```{r}
d$high_fidelity <- d$fidelity > median(d$fidelity)

@@

outcomes <- bind_rows(replicated, turk, fidelity, open_materials) 
names(outcomes) <- c("No","Partial","Full", "Mediator","Value")
outcomes <- outcomes %>%
  select(Mediator, Value, No, Partial, Full)
```
